Digital History in Finland, 1488-1828

### 2016-06-14 inst/examples/20160303-Krakow.Rmd

#jpeg("20160303-paper.jpeg", quality = 100, height = 300, width = 480)
pdf("20160303-paper.pdf", width = 12, height = 9)
print(p)
dev.off()

p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity", color = "black") +
     ggtitle("Title count") +
     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     scale_fill_grey() +
     guides(fill = guide_legend(reverse = TRUE)) +      
     xlab("Publication decade") + ylab("Title count (n)")
print(p)

@@

```

>>>>

pdf("20160303-paper.pdf", width = 12, height = 9)
print(p)
dev.off()

jpeg("20160303-paper.jpg", quality = 100, height = 480, width = 600)
print(p)
dev.off()

p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity", color = "black") +
     ggtitle("Title count") +
     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     scale_fill_grey() +
     guides(fill = guide_legend(reverse = TRUE, title = "")) +      
     xlab("Publication decade") + ylab("Title count (n)")
print(p)

@@

jpeg("20160303-titles.jpg", quality = 100, height = 480, width = 600)
print(p)
dev.off()
```
